CS6999 Web Data and Text Mining:\\Parallel Text Indexer Project Report

### 2011-05-15 report/report.tex
Started literature survey

The Aho-Corasick string matching algorithm\cite{RefWorks:103} is a
kind of dictionary matching search algorithm that constructs a finite
state machine to scan for a given set of keywords. It is, in effect, a
reduced grammar regular expression parser described in
\cite{RefWorks:111}.

>>>>

\textbf{Evalauation}\\
In the case of machine learning and classification systems, the
specification of a particular set of misclassification costs or false
and positive misclassification rates define a particular
\textit{operating point} of the system. This concept applies equally
to \textit{information retrieval} systems whereby it is misleading to
represent the operating characteristics of a particular system by a
single scalar metric.  Non-scalar evaluation methods try to
characterize the performance of a system over a range of operating
conditions. Although this makes direct performance comparisons
ambiguous, we are more likely to be able to select the algorithm which
will perform best in the real world by applying domain expertise to
the results of a non-scalar evaluation \cite{RefWorks:32}.

\textbf{Aho-Corasick}\\
In order to construct an \textit{inverted index}, documents must be
scanned to determine \termit{term frequencies}. The Aho-Corasick
string matching algorithm\cite{RefWorks:103} is a simple and efficient
text scanning algorithm. The algorithm constructs a finite
state machine to scan for a given set of keywords. It is, in effect, a
reduced grammar regular expression parser described in
\cite{RefWorks:111}. The algorithm is simple and efficient,
construction time being proportional to the sum of the length of the
keyword set, and the number of state trasitions required to scan a
document is independent of the number of the size of the keyword
set.

\textbf{Parallelization}\\
Once an objective measure has been established, the performance of an
information retrieval system can be improved iteratively by making
various optimizations. These optimizations may take the form of
algorithmic enhancements, implementation efficiencies, or
parallelization.

Algorithmic enhancements usually represent the forefront of research
in the field. Initial work to validate a new concept or algorithm is
usaully performed in a very controlled environment and on relatively
small document collections. As the field matures, improvements are
harder fought and often involve increasingly complex algorithms
and corpus approximation methods into which it becomes more difficult
to \textit{fold-in} new documents. In addressing the considerable
computation cost of re-calculating \textit{LSI} approximations,
\cite{RefWorks:101} introduced new update methods which saw
improved average precisions but were forced to conclude that the
improvements were at a computational premium over previous methods.

Enhancement of implementation efficiency in
\cite{RefWorks:96} saw a six-fold timing improvment in \textit{LSI}
searches on large document collections. The same study achieved nearly
180 times improvement through the use of parallelization. The study
made no algorithmic improvements and serves to re-inforce the fact that
parallelization is an important mechanism employed by large commercial
systems to cope with the ever increasing bodies of data that must be
processed.
